---
title: "Getting Started with pressR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with pressR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4,
  dpi = 96
)
```

```{r setup, message=FALSE}
library(pressR)
```

## What pressR does

**pressR** parses, analyzes, and visualizes pressure distribution data
from capacitive sensor systems such as novel emed®, pedar®, and
pliance®. It provides:

* Predefined sensor layouts (in-shoe, platform, saddle, seating, glove),
* Parsers for the novel ASCII export format and generic CSV,
* A full analysis pipeline (per-frame metrics, trial summaries,
  regional analysis, gait-cycle detection, saddle-fit checks),
* `ggplot2`-based visualization and composite reports,
* An interactive Shiny application for data exploration.

> **Disclaimer.** pressR is not affiliated with novel GmbH. Product
> names (emed, pedar, pliance, loadsol) are used for identification
> only.

## Load a layout

Every trial is tied to a `pr_layout` object that describes the sensor
geometry. For example, the pedar in-shoe insole:

```{r}
layout <- pr_layout_pedar()
print(layout)
```

## Generate a synthetic example trial

`pr_example_trial()` produces realistic synthetic data for each
supported application. This is useful for quick demos, tests, and
vignettes.

```{r}
trial <- pr_example_trial("pedar")
trial
```

## Visualize

The default plot method draws a maximum-pressure picture (MPP):

```{r, fig.alt="MPP heatmap of the synthetic pedar trial"}
pr_plot_heatmap(trial)
```

Time-domain curves are equally straightforward:

```{r, fig.alt="Force vs time with gait cycles shaded"}
pr_plot_force_time(trial, show_cycles = TRUE)
```

## Summarize

`pr_summary()` returns a single-row tibble containing the common
biomechanical parameters:

```{r}
pr_summary(trial)
```

## Regional analysis

With the pedar layout's default region masks you get one row per
anatomical region:

```{r}
pr_calc_regional(trial)
```

## Export

Results can be exported as CSV:

```{r, eval=FALSE}
tmp <- tempfile(fileext = ".csv")
pr_export_csv(trial, tmp, what = "summary")
```

## Launch the Shiny app

```{r, eval=FALSE}
pr_run_app(trial)
```
